Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-16 survey/survey.tex
citations and small subsection

@@

We develop an arrow meta-language to encapsulate information
effects. This metalanguage serves to encapsulate effects, in much the
same way that traditional arrows or monads serve to encapsulate
effects over the \lcal.

new paper \url{https://arxiv.org/pdf/1805.08605.pdf}

>>>>

By insisting on a computational model that explicitly enforces  
conservation of information \ldots

@@

A computational model that enforces the principle of conservation of
information is arguably \emph{richer} than a conventional model that
cannot even express the notion of information. Practically the
conventional model is easily recovered by simply adding constructs
that intentionally and explicitly create or erase information. Such
constructs allow one to recover the classical perspective with the
added advantage that it is possible to reason about such creation and
erasure of information using type and effect systems, monads, or
arrows~\cite{infeffects,inversearrows}.
